---
title: "**Text Mining and Topic Modeling: with special application to central banks**"
author: "Gustavo Rojas-Matute"
date: "1/25/2021"
output: pdf_document
institution: "American University"
bibliography: Topic_Modeling.bib
---

```{r setup, include=FALSE, echo=  FALSE, message=FALSE,  warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 
Text mining, data and analysis have been becoming in power tools in economics. For instance, creating a news-based uncertainty index or sentiment analysis in forecasting. In monetary policy, text mining could help us to understand if the central bank pays more attention to inflation than unemployment or vice-verse. 

The goal of this tutorial is to learn how to extract, store, clean and analyze data from publications of the Federal Reserve.  

## What we need 
We will need the following packages: 
```{r, message=FALSE,  warning=FALSE}
library(tidyverse)
library(pdftools)
library(stringi)
require(topicmodels)
library(quanteda)
library(tidytext)
library(xml2)
```
## Getting start with a simple Text Extraction 

Let's start by extracting a PDF text from the Federal Reserve web. This is a document from the Federal Open Market Operations Committee published on July 3rd of 1996. Since this is a PDF document, we use the pdf_text function: 


```{r,message=FALSE,  warning=FALSE}

omc0796 <- pdf_text("https://www.federalreserve.gov/monetarypolicy/files/FOMC19960703meeting.pdf")

```
Maybe you want to explore the document by typing: 

```{r,  results='hide'}
writeLines(as.character(omc0796))
```

But our main interest is not the complete text, but the analysis of the words. This is why to need to organize the document. There are different approaches using corpus or dfm, but here we will use data frame. 

```{r, message=FALSE,  warning=FALSE}
corpus_fed <- data_frame(word=stri_trans_tolower(unlist(stri_extract_all_words(omc0796))),
                         count=1)
corpus_fed[1:10,1] 
```
As we can see, our data frame organizes every word of the document, including numbers, stop words and punctuation. This something we will tackle later. 

But with this data frame, we can count the number of words and estimate the cumulative words. Suppose we want to investigate: "inflation", "cpi", "growth", "gdp", "unemployment". Here is an example with the first ten rows: 

```{r}

corpus_fed$word_number <- 1:nrow(corpus_fed)
cumsum_corpus_fed <- mutate(group_by(corpus_fed, word), cumsum=cumsum(count))
filter_fed <- filter(cumsum_corpus_fed, word %in% c("inflation", "cpi", "growth", "gdp", "unemployment"))

cumsum_corpus_fed[1:10,]
```

Now we are able to plot: 

```{r}

gg_fed <- ggplot(filter_fed,
                 aes(x=word_number, y=cumsum))
gg_fed <- gg_fed + geom_line(aes(color=word), size=0.75) + 
  geom_point(aes(fill=word), shape=21, color="white", size=1.5) + 
  scale_x_continuous(limits=c(1, nrow(corpus_fed)))+
  theme_bw() +
  ylab("Cumulative") +
  xlab("Word number")
gg_fed
```

## Organizing and storing with Tibble

Another approach to organize the text in a data frame is using tibble (also the function dtm - document to matrix). We can organize the original document omc0796 using tibble function as follows: 

```{r, message=FALSE,  warning=FALSE}
library(dplyr) # Tibble is a data frame
text_df <- tibble(line = 1:115, text = omc0796)

```


## Cleaning using Tidytext 
As mentioned above, in any text there are always characters that are not informative such as stop words (the, in, of, etc), numbers and punctuation. 

It is possible to remove them: 
```{r message=FALSE,  warning=FALSE}

library(tidytext) ## this is equivalent to data_frame (corpus_fed)

fed_df <- text_df %>% unnest_tokens(word, text) ## unnest_tokens convert to lowercase 

## Remove stop words

data(stop_words)

clean_text_fed <- fed_df %>%   anti_join(stop_words) %>% mutate(word = gsub("[[:digit:]]","", word)) #REMOVE NUMBERS
  


```

## Frequency of words

Now that we have cleaned the data, we can plot a frequency of words: 

```{r}

library(ggplot2)

clean_text_fed %>%
  count(word, sort = TRUE) %>%
  filter(n > 100) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL)
```


## Word Cloud 

We can also plot a word cloud:

```{r, message=FALSE, warning=FALSE}
library(wordcloud)

clean_text_fed  %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))

```


## Sentiment Analysis 

Finally, we can conduct sentiment analysis and the contribution of every word to the sentiment. 

```{r message = FALSE, warning= FALSE}
bing <- get_sentiments("bing")

sentiment_fed <- clean_text_fed  %>%
  inner_join(bing) %>%
  count(word, sentiment, sort = TRUE)

sentiment_fed %>% # sentiment contribution 
  filter(n > 20) %>%
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col() +
  coord_flip() +
  labs(y = "Contribution to sentiment")

```


## Working with multiples documents 
Now it is time to learn how to work with multiple documment at the same time. There are several examples on how to work with data sets in R, but here we will focused on how to extract and analyze press realeses from the Federal Reserve. 

First, lets build a vector of the links we want to analyze.  


```{r}
## List of documents 

links<-c("https://www.federalreserve.gov/newsevents/pressreleases/monetary20190130a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20190320a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20190501a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20180131a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20180321a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20180502a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20180613a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20180801a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20180926a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20181108a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20181219a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20170201a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20170315a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20170503a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20170614a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20170726a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20170920a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20171101a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20171213a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20160127a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20160316a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20160427a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20160615a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20160727a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20160921a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20161102a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20161214a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20150128a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20150318a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20150429a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20150617a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20150729a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20150917a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20151028a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20151216a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20140129a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20140319a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20140430a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20140618a.htm", 
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20140730a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20140917a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20141029a.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20141217a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20130130a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20130320a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20130501a.htm", 
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20130619a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20130731a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20130918a.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20131030a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20131218a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20120125a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20120313a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20120425a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20120620a.htm", 
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20120801a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20120913a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20121024a.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20121212a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20110126a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20110315a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20110427a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20110622a.htm", 
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20110809a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20110921a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20111102a.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20111213a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20100127a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20100316a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20100428a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20100623a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20100810a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20100921a.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20101103a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20101214a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20090128a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20090318a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20090429a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20090624a.htm", 
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20090812a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20090923a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20091104a.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20091216a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20080122b.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20080130a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20080318a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20080430a.htm", 
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20080625a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20080805a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20080916a.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20081008a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20081029a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20081216b.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20070131a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20070321a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20070509a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20070618a.htm", 
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20070807a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20070817b.htm",  
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20070918a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20071031a.htm",
         "https://www.federalreserve.gov/newsevents/pressreleases/monetary20071211a.htm"
)


```

What we need:

```{r message=FALSE, warning=FALSE}
library(rvest)
library(purrr)
library(stringr)

```


Since these documents are in html format, the process is similar to web scraping, link by link. Here is a useful approach to do it. 

```{r}

out <- vector("character", length = length(links))
for(i in seq_along(links)){
  derby <- read_html(links[i])
  out[i] <- derby %>%
    html_node("body") %>%
    html_text() %>% 
    stri_trim()
}

```

A simple way to organize the documents using dfm and tidy: 

```{r}
myFOMC_td <- tidy(quanteda::dfm(out, verbose = FALSE))
```

If we want, it is possible to analyze directly some topics. For instance, suppose we are interested in analyze "inflation" and "employment". Here is an example on how to count both words among the different texts (links) we have: 


```{r, message=FALSE, warning=FALSE}

inflation <-  myFOMC_td %>%
  filter(term %in% c("inflation")) 
inflation[1:10,]

employment <-  myFOMC_td %>%
  filter(term %in% c("employment")) 
employment[1:10,]


```

If we want to plot the evolution of the counts of both "inflation" and "employment" in the time, we need to create a vector with the dates the press relaeses were published: 
```{r}

library(lubridate)

statement.dates<-NULL
year<-NULL
for(i in seq(from=1, to=length(links))) {
  statement.dates[i]<-(str_extract(links[i],"[[:digit:]]+"))
  year[i]<-substr(statement.dates[i],1,4)
}

reports<-data.frame(year,statement.dates, links)

reports %<>% mutate_if(is.factor, as.character)%>% arrange(statement.dates)

time_FOMC <- as.Date(reports$statement.dates, format = "%Y%m%d")
```

Now, let's plot them: 

```{r}

data_FOMC <- data.frame(time_FOMC[1:101], inflation$document, inflation$count, employment$count[1:101])

  ggplot(data =  data_FOMC, aes(time_FOMC.1.101., inflation.count, colour = "inflation")) +
  geom_point() +
  geom_smooth() +
  xlab("") +
  ylab("Count")
  

  ggplot(data = data_FOMC, aes(x = time_FOMC.1.101., y = employment.count.1.101., colour = "employment"))  + 
    geom_point() +
    geom_smooth() +
    xlab("") +
  ylab("Count")
```


## Sentiment analysis 

We can also conduct sentiment analysis. Here we can observe the net sentiment (positive - negative) per text: 
```{r}

myFOMC_sent <- myFOMC_td %>% inner_join(get_sentiments("bing"), by = c(term = "word"))

sentiment_per_text<- myFOMC_sent %>%
  dplyr::count(document, sentiment, wt = count) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative) %>%
  arrange(sentiment)

sentiment_per_text[1:10,]
```

## Cleaning the data

To be more efficient in topic modeling, it is helpful to clean the data by removing uninformative characters such as punctuation and stop words. 

```{r}
#cleaning
clean_FOMC <- myFOMC_td %>% 
  anti_join(stop_words, by = c(term = "word")) %>%
  mutate(term = gsub("[[:punct:]]","", term)) %>% 
  mutate(term = gsub("-","", term)) %>%
  mutate(term = gsub(" ","", term))
```

## Topic Modeling 
Now that we have cleaned the data, we can conduct topic modeling. We will use the LDA algorithm. We first start the number of topics we want to identify. For instance, by setting k = 2, we want to identify two topics. The following table shows us the words related which topics 1 and 2. 

```{r, message=FALSE, warning=FALSE}
myFOMC_dtm <- clean_FOMC %>% cast_dtm(document, term, count) 
myFOMC_LDA <- LDA(myFOMC_dtm, k = 2, control = list(seed = 1234))
mytopics<-  tidy(myFOMC_LDA , matrix = "beta")

mytopics_terms <- mytopics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

mytopics_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()


```

```{r}
beta_spread <- mytopics %>%
  mutate(topic = paste0("topic", topic)) %>%
  spread(topic, beta) %>%
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_ratio = log2(topic2 / topic1))
beta_spread

```

```{r, message=FALSE, warning=FALSE}
myFOMC_dtm <- clean_FOMC %>% cast_dtm(document, term, count) 
myFOMC_LDA <- LDA(myFOMC_dtm, k = 4, control = list(seed = 1234))
mytopics<-  tidy(myFOMC_LDA , matrix = "beta")

mytopics_terms <- mytopics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

mytopics_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()


```
## Further literature

@Benchimol2020 have a great working paper on text mining focused on central banks. 
@Julia2020 have great tools fro text mining. 
## **References**
